Bayesian Deep Gaussian Processes for Correlated Functional Data: \\ A Case Study in Cosmological Power Spectra

### 2025-06-13 paper/main.tex
include Sigma_epsilon details, more info on CAMB, *HM to *FCO, etc.

Let $S$ represent the true (but unknown) underlying power matter spectrum for
a particular cosmology.  We consider $\bar{Y}$ a noisy realization of $S$.
Specifically, we assume $\bar{Y}$ is a random realization of a Gaussian 
process centered at $S$ with some covariance, i.e., 
$\bar{Y}\mid S \sim \mathrm{GP}(S, \Sigma_\varepsilon)$.  While previous works
have considered diagonal $\Sigma_\varepsilon$ \citep{moran2024dpc}, we find it
essential to account for the smoothly varying spatial dependence of the
low resolution runs (as visualized in Figure \ref{fig:plot_data}).  For
this, we embrace variations of the Mat\'ern kernel \citep{stein1999interpolation},
tailored to each scenario (more on this in later subsections).
We consider $\Sigma_\varepsilon$ as known, given domain-matter expertise.
\textcolor{red}{(Here, we are fixing $\Sigma_\varepsilon$ upon estimating the Matern 
parameters and utilizing the precision estimates (domain-matter expertise from 
log-log regression model)?  The estimate of $\Sigma_\varepsilon$ is tailored for
each cosmology, as the Matern estimates are computed uniquely for each.)}

@@

We use the Mat\`ern kernels,
\[
\begin{aligned}
&\Sigma_S(W)^{i,j} = \tau^2 \left( 1 + \frac{\sqrt{5}d}{\sqrt{\theta_S}} + 
  \frac{5d^2}{3\theta_S}\right) \exp\left(-\frac{\sqrt{5}d}{\sqrt{\theta_S}}\right)
\quad\textrm{for}\quad 
d=||w_i-w_j||^2, \;\;\textrm{and} \\
&\Sigma_W(X)^{i,j} = \left( 1 + \frac{\sqrt{5}d}{\sqrt{\theta_W}} + 
  \frac{5d^2}{3\theta_W}\right) \exp\left(-\frac{\sqrt{5}d}{\sqrt{\theta_W}}\right)
\quad\textrm{for}\quad 
d=||x_i-x_j||^2.
\end{aligned}
\]
In the $S$ layer, hyperparameters $\tau^2$ and $\theta_S$ govern the 
correlation scale and lengthscale respectively.  In the $W$ layer, we allow for a
unique lengthscale $\theta_W$ but enforce unit scale following \citet{sauer2023active}.

@@

Given burned-in posterior samples $\{W^{(t)}, \tau^{2(t)}, \theta_S^{(t)}, \theta_W^{(t)}\}$
for $t\in\mathcal{T}$, we may obtain the
posterior distribution of the true power matter spectra for a particular cosmology as
\[
S^{(t)}\mid\bar{Y}, \Sigma_\varepsilon \sim \mathcal{N}_n(m^{(t)}, C^{(t)})
\quad\textrm{where}\quad
\begin{array}{rl}
C^{(t)}&=\left(\Sigma_S(W^{(t)})^{-1}+\Sigma_\varepsilon^{-1}\right)^{-1} \\
m^{(t)}&=C^{(t)}\left(\Sigma_\varepsilon^{-1}\bar{Y}+\Sigma_S(W^{(t)})^{-1}\boldsymbol{\mu}\right).
\end{array}
\]

These results come from Bayes' Theorem, with details of this derivation provided 
in \ref{sec:apdx_SgivenY}. With all posterior draws $S^{(t)}$, we compute
the average of these to obtain our posterior mean for a particular cosmology. Additionally,
we quantify uncertainty by finding the 2.5th and 97.5th percentiles of the posterior 
draws at each index to obtain a 95\% credible interval.
We denote our inference procedure for the hierarchical model of Eq.~\ref{eq:dgphm} as
``DGP.HM'' given its deep Gaussian process foundation with additional hierarchical modeling (HM)
structure to incorporate multiple functional outputs.

@@

We compare DGP.HM to competing models with a simulation study where the underlying 
true curve is known. Following \cite{moran2024dpc}, we consider two functions 
($f_1$ and $f_2$) each with two variance specifications (settings ``4" and ``5", 
\textcolor{magenta}{we can consider additional homoskedastic cases in the appendix if necessary}).

@@

For the two variance settings, we consider matrices $\Sigma_4$ and $\Sigma_5$ to 
have a Mat\'ern covariance function with a nugget of $10^{-8}$ and smoothness of 2.5. 
For setting ``4", we have $\tau^2=0.0225$ and $\theta=0.01$. For setting ``5", we have 
$\tau^2=0.01$ and $\theta=0.05$, and additionally scale this covariance matrix by 
a vector of values $s$ so that $\Sigma_5 = s M s^T$ is nonstationary; here $M$ is 
a Mat\'ern covariance matrix with parameters $\tau^2$ and $\theta$.

@@

The metrics we use to evaluate performance are mean squared error (MSE) and the 
log score, a proper scoring rule which takes both prediction and intervals into 
consideration \citep{gneiting2007strictly}. For both metrics, a lower value indicates 
better performance. Log score and MSE results are shown in Figures \ref{fig:sims_logS} 
and \ref{fig:sims_MSE} respectively; our DGP.HM model performs favorably against 
these current benchmark methods. \textcolor{magenta}{If we mention that DGP.HM timings 
speed up compared to \texttt{deepgp}, we would also need to mention that \texttt{hetGP} 
is much faster than both of these.}

@@

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{CAMB_fit_model1.png}
    \caption{Example of DGP.HM model fit for the first batch of model runs from the CAMB data, 
             with LOESS mean term subtracted. We can compare the orange lines 
             (posterior mean and dotted 95\% credible interval) to the light blue line,
             representing the infinite-resolution ``true" spectrum.}   
    \label{fig:fit_camb}
\end{figure}

We use 32 CAMB batches to train the DGP.HM model and reserve the other 32 as a test set.
To imitate the role of the perturbation theory output of Mira-Titan, we anchor estimates of the CAMB
power spectrum at the infinite-resolution for $\log_{10}(k) < -1.7$, and then rely 
strictly on the low- and high-resolution runs for $k$ above this. We take a weighted
average of the CAMB runs and assume heteroskedastic errors in a similar fashion. For the CAMB
data, lengthscale estimates are consistently around $3\times 10^{-7}$, evidence that we
can simplify our covariance structure to contain no spatial dependence 
(compare low-resolution runs of Figure \ref{fig:fit_camb} 
with Figure \ref{fig:plot_data}).

@@

From plots of the multiple low-resolution spectra (e.g., Figure \ref{fig:plot_data}), 
we find they vary smoothly about some mean $S$, suggesting that a dense covariance 
matrix $\Sigma_\varepsilon$ (accounting for spatial dependence) may outperform a 
diagonal covariance $\Lambda_\ell^{-1}$ for $\bar Y$. In previous work, we have 
modeled multiple candidates for $\Sigma_\varepsilon$ \citep{walsh2023bayesian} and 
found that a Mat\'ern covariance $\Sigma_\ell$ trained on the low-resolution runs 
(pre-scaled by the precision values and subtracting a LOESS-smoothed average) performs 
the best. We specify this structure within $\Sigma_\varepsilon$ and refer readers 
to \cite{walsh2023bayesian} for a more detailed exposition. This yields 
$\Sigma_\varepsilon=\left(\Lambda_p^{-1} + \Sigma_\ell + \Lambda_h^{-1}\right)^{-1}$, 
where $\Lambda_p, \Sigma_\ell^{-1}, \text{ and } \Lambda_h$ are all $n\times n$ 
and are 0 wherever the corresponding data type is biased.

From here, we estimate $\tau_\ell, \theta_\ell$ with maximum 
likelihood, and conditional on $\Sigma_\varepsilon$,

@@

For simplicity, we will denote these eight parameters as $\psi \in \mathbb{R}^8$.

Upon obtaining the posterior means from each of the 111 training cosmologies, this 
section details our second contribution - the use of the Bayesian DGP.HM model 
to predict the curve for held-out cosmologies. This is achieved with modeling the 
weights of different basis functions as GPs.

@@

Figure \ref{fig:mean_PCs_oneW} illustrates this decomposition with the estimated 
mean trend, the principal components contained in $B$, and one example of how the 
weight for the first PC will vary dependent on the first of $p_\psi=8$ cosmological 
parameters contained in $\psi$.

@@

From our 32 posterior means using DGP.HM, these are input into SEPIA in order to predict power spectra
for the 32 test cosmologies. With the infinite-resolution output, we have a sense of the ``best-case" 
predictions we can have (i.e., if we trained with the 32 true power spectra, as opposed to our 
estimated posterior means). In Figure \ref{fig:pca_preds_v_camb}, we see comparisons of the heldout 
infinite resolution alongside two predictions: one based on DGP.HM and the ``best-case" scenario using the
infinite-resolution spectra of the training set. There is a high level of agreement between the pairs
of predictions across cosmologies. Upon comparing MSEs for each of these prediction scenarios 
(Figure \ref{fig:mse_camb}, most are very similar across the two groups (with the two most difficult 
predictions being the exceptions), suggesting that overall DGP.HM is estimating the true spectra 
for each batch well.

\begin{figure}
    \centering
    \includegraphics[width=4in]{preds_diff1_4_8.jpg}
    \caption{Predictions for 16 of the 32 test cosmologies after centering and scaling. 
             The interpolated infinite resolution run is shown in black, the prediction 
             (trained on the infinite resolution) is in blue and the prediction from 
             the DGP.HM posterior mean is in red.}   
    \label{fig:pca_preds_v_camb}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=3in]{mse_dot.jpg}
    \caption{Comparison of MSE for CAMB predictions, when training with DGP.HM posterior 
             means (left), and training with the ``true" infinite-resolution spectra (right).}   
    \label{fig:mse_camb}
\end{figure}

@@

Both Cosmic Emu and DGP.HM are capable of modeling a true underlying functions based 
upon multiple functional realizations, but our approach utilizes DGPs within a 
hierarchical model in lieu of deep process convolutions. After obtaining the estimated 
smooth spectra from the training cosmologies, each method utilizes GPs in order to 
estimate the weights of the PCs from the estimated spectra. Below, we compare prediction 
performance between Cosmic Emu and DGP.HM for the 6 held-out cosmologies. 
\textcolor{magenta}{In addition, we can also predict over a large uniform or full 
factorial design to obtain estimated main effects for each cosmological parameter in 
$\psi$, interactions amongst the $p_\psi=8$ parameters, and decompose the overall 
variation by main effects, two-way interactions, and so on. Should this be included?}

Plots for the average root mean squared error (RMSE) for each prediction method over the 
6 cosmologies and each $k$ value are shown in Figure \ref{fig:plot_rmse_k}. Comparisons 
of the spectrum estimation for training cosmologies are shown as well (using RMSE against 
the weighted average of observations). For predictions, DGP.HM achieves the greatest 
reduction in RMSE in the region where perturbation theory and the low-resolution runs 
are deemed unbiased. For the region where only the high-resolution run is unbiased, 
Cosmic Emu has a lower average RMSE. Over all $k$ values and predictions, DGP.HM has 
an average RMSE of 0.0089 and Cosmic Emu has an average RMSE of 0.0106. Our RMSE is 
lower at 56\% of $k$ values considered. The individual predictions for each method and 
cosmology are shown in Figure \ref{fig:plot_pred_1to6}.

@@

Multiple avenues for future research emerge: in addition to estimating dark matter 
power spectra, batches of hydrodynamical simulations exist, and this method could 
easily be adapted to handle such datasets. Other applications outside of cosmology 
can be explored, wherever multiple functional outputs exist, perhaps with spatial 
correlation (for example, observing multiple tropical cyclone forecasts). More detailed 
sensitivity analyses for the cosmological parameters can be explored to gain insights 
into how each of these parameters interact, and which are most significant. From a 
modeling perspective, changes to the model could include modeling the latent layer 
$W$ jointly across different cosmologies, as well as considering different redshift 
values other than $z=0$. Leveraging a hybrid model between DGP.HM and Cosmic Emu 
may also help to obtain accurate estimates on the lower and higher ends of $k$ values, 
respectively. Additionally, Bayesian smoothing spline ANOVA (BSS-ANOVA) or other methods 
could be compared in addition to DGPs.

@@

\begin{figure}[ht]
    \centering
    \includegraphics[width=6in]{pred_1to6.png}
    \caption{Results of all six predictions for both methods on the held-out 
    cosmologies (weighted average subtracted). CosmicEMU is dashed, DGP.HM is dotted, 
    and solid gray lines show results of held-out computer model runs.}
    \label{fig:plot_pred_1to6}
\end{figure}

>>>>

Let $S$ represent the true (but unknown) underlying power matter spectrum for
a particular cosmology.  We consider $\bar{Y}$ a noisy realization of $S$.
Specifically, we assume $\bar{Y}$ is a random realization of a Gaussian 
process centered at $S$ with some covariance, i.e., 
$\bar{Y}\mid S \sim \mathrm{GP}(S, \Sigma_\varepsilon)$.  While previous works
have considered diagonal $\Sigma_\varepsilon$ \citep{moran2024dpc}, we find it
essential to account for the smoothly varying spatial dependence of the
low resolution runs (as visualized in Figure \ref{fig:plot_data}).  For
this, we specify a dense covariance matrix $\Sigma_\varepsilon$ that simulataneously
allows us to model the correlated errors, as well as build domain-matter expertise
into the prior. To this end, we embrace variations of the Mat\'ern kernel 
\citep{stein1999interpolation}, tailored to each cosmology (more on this in later 
subsections).

@@

We use the Mat\`ern kernel \textcolor{red}{@Annie, might need to add/remove $\tau^2$ 
in one or both of these kernels},
\[
\begin{aligned}
&\Sigma_S(W)^{i,j} = \tau^2 \left( 1 + \frac{\sqrt{5}d}{\sqrt{\theta_S}} + 
  \frac{5d^2}{3\theta_S}\right) \exp\left(-\frac{\sqrt{5}d}{\sqrt{\theta_S}}\right)
\quad\textrm{for}\quad 
d=||w_i-w_j||^2. 
% \;\;\textrm{and} \\
% &\Sigma_W(X)^{i,j} = \left( 1 + \frac{\sqrt{5}d}{\sqrt{\theta_W}} + 
%   \frac{5d^2}{3\theta_W}\right) \exp\left(-\frac{\sqrt{5}d}{\sqrt{\theta_W}}\right)
% \quad\textrm{for}\quad 
% d=||x_i-x_j||^2,
\end{aligned}
\]
In the $S$ layer, hyperparameters $\tau^2$ and $\theta_S$ govern the correlation 
scale and lengthscale respectively.  In the $W$ layer, $\Sigma_W(X)^{i,j}$ is defined 
analogously for squared distances $d=||x_i-x_j||^2$ and we allow for a unique 
lengthscale $\theta_W$ but enforce unit scale following \citet{sauer2023active}.

@@

Given burned-in posterior samples $\{W^{(t)}, \tau^{2(t)}, \theta_S^{(t)}, \theta_W^{(t)}\}$
for $t\in\mathcal{T}$, we may obtain the
posterior distribution of the true power matter spectra for a particular cosmology as
\[
S^{(t)}\mid\bar{Y}, \Sigma_\varepsilon \sim \mathcal{N}_n(m^{(t)}, C^{(t)})
\quad\textrm{where}\quad
\begin{array}{rl}
C^{(t)}&=\left(\Sigma_S(W^{(t)})^{-1}+\Sigma_\varepsilon^{-1}\right)^{-1} \\
m^{(t)}&=C^{(t)}\left(\Sigma_\varepsilon^{-1}\bar{Y}\right).
% "+\Sigma_S(W^{(t)})^{-1}\boldsymbol{\mu}" removed from m^t when mu=0
\end{array}
\]

These results come from Bayes' Theorem and reflect that $\boldsymbol{\mu}_S=\boldsymbol{0}$. 
These results will generalize to any value for $\boldsymbol{\mu}_S$, with details of this 
general derivation provided in \ref{sec:apdx_SgivenY}. With all posterior draws $S^{(t)}$, we compute
the average of these to obtain our posterior mean for a particular cosmology. Additionally,
we quantify uncertainty by finding the 2.5th and 97.5th percentiles of the posterior 
draws at each index to obtain a 95\% credible interval.
We denote our inference procedure for the hierarchical model of Eq.~\ref{eq:dgphm} as
``DGP.FCO'' given its deep Gaussian process foundation with additional hierarchical modeling
structure to incorporate multiple functional correlated outputs (FCO).

@@

We compare DGP.FCO to competing models with a simulation study where the underlying 
true curve is known. Following \cite{moran2024dpc}, we consider two functions 
($f_1$ and $f_2$) each with two variance specifications (settings ``A" and ``B", 
\textcolor{magenta}{we can consider additional homoskedastic cases in the appendix if necessary}).

@@

For the two variance settings, we consider matrices $\Sigma_A$ and $\Sigma_B$ to 
have a Mat\'ern covariance function with a nugget of $10^{-8}$ and smoothness of 2.5. 
For setting ``A", we have $\tau^2=0.0225$ and $\theta=0.01$. For setting ``B", we have 
$\tau^2=0.1$ and $\theta=0.05$, and additionally scale this covariance matrix by 
a vector of precision values $s$ so that $\Sigma_B = s M s^T$ is nonstationary; here $M$ is 
a Mat\'ern covariance matrix with parameters $\tau^2$ and $\theta$.

@@

The metrics we use to evaluate performance are mean squared error (MSE) and the 
log score, a proper scoring rule which takes both prediction and intervals into 
consideration \citep{gneiting2007strictly}. For both metrics, a lower value indicates 
better performance. Log score are shown in Figure \ref{fig:sims_logS}; our DGP.FCO 
model performs favorably against each of these current benchmark methods by
accounting for spatial dependence within our model, resulting in more accurate UQ.
MSE results, which do not address UQ, were comparable across competing methods; these results
can be found in Figure \ref{fig:sims_MSE}. \textcolor{magenta}{If we mention that DGP.FCO timings 
speed up compared to \texttt{deepgp} and DPC, we would also need to mention that \texttt{hetGP} 
is much faster than all of these.}

@@

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{CAMB_fit_model1.png}
    \caption{Example of DGP.FCO model fit for the first batch of model runs from the CAMB data, 
             with LOESS mean term subtracted. We can compare the orange lines 
             (posterior mean and dotted 95\% credible interval) to the light blue line,
             representing the infinite-resolution ``true" spectrum.}   
    \label{fig:fit_camb}
\end{figure}

We use 32 CAMB batches to train the DGP.FCO model and reserve the other 32 as a test set.
To imitate the role of the perturbation theory output of Mira-Titan, we anchor estimates of the CAMB
power spectrum at the infinite-resolution for $\log_{10}(k) < -1.7$, and then rely 
strictly on the low- and high-resolution runs for $k$ above this. We take a weighted
average of the CAMB runs and assume heteroskedastic errors in a similar fashion.

We use a log-log regression model to obtain precision estimates $\Lambda_\ell$ and $\Lambda_h$
for the low- and high-resolution runs respectively, as outlined in Section \ref{sec:data}. 
Similarly, we set $\Lambda_i=10^8$ to illustrate high confidence in the infinite-resolution 
run for low $k$ values and incorporate these estimates within $\Sigma_\varepsilon$. 
With the precision information, we then estimate the Mat\'ern parameters for 
$\Sigma_\varepsilon$. For the CAMB data, lengthscale estimates are consistently 
around $3\times 10^{-7}$, evidence that we can simplify our covariance structure 
to contain no spatial dependence (compare low-resolution runs of Figure \ref{fig:fit_camb} 
with Figure \ref{fig:plot_data}). We therefore specify $\Sigma_\varepsilon = 
(15\Lambda_\ell+\Lambda_h+\Lambda_i)^{-1}$ for the CAMB data.

After fitting the DGP.FCO model, an illustration of the posterior mean and its UQ can
be seen in Figure \ref{fig:fit_camb}. Notice that there are peaks where both the high-resolution
run and the weighted average are biased, but our posterior mean adjusts appropriately 
and has a more reliable estimate for the infinite-resolution run (the ``truth" in this setting). 
UQ is handled well, as precision increases with increasing $k$, which is captured in our
95\% credible intervals.

@@

From plots of the multiple low-resolution spectra (e.g., Figure \ref{fig:plot_data}), 
we find they vary smoothly about some mean $S$, suggesting that a dense covariance 
matrix $\Sigma_\varepsilon$ (accounting for spatial dependence) may outperform a 
diagonal covariance $\Lambda_\ell^{-1}$ for $\bar Y$. From Section \ref{sec:data},
we can incorporate domain knowledge from $\Lambda_p, \Lambda_\ell,$ and $\Lambda_h$ 
within our model. In previous work, we have modeled multiple candidates for 
$\Sigma_\varepsilon$ \citep{walsh2023bayesian} and found that a Mat\'ern covariance 
$\Sigma_\ell$ trained on the low-resolution runs (pre-scaled by the precision 
values and subtracting a LOESS-smoothed average) performs the best. 
We specify this structure within $\Sigma_\varepsilon$ and refer readers 
to \cite{walsh2023bayesian} for a more detailed exposition. This yields 
$\Sigma_\varepsilon=\left(\Lambda_p^{-1} + \Sigma_\ell + \Lambda_h^{-1}\right)^{-1}$, 
where $\Lambda_p, \Sigma_\ell^{-1}, \text{ and } \Lambda_h$ are all $n\times n$ 
and are 0 wherever the corresponding data type is biased. From here, we estimate 
$\tau_\ell, \theta_\ell$ with maximum likelihood, and input these within 
$\Sigma_\varepsilon$, which we use as an input to our model.

@@

Upon obtaining the posterior means from each of the 111 training cosmologies, this 
section details our second contribution - the use of the Bayesian DGP.FCO model 
to predict the curve for held-out cosmologies. This is achieved with modeling the 
weights of different basis functions as GPs.

@@

Our goal is to predict the power spectrum for a held-out cosmology. 
For simplicity, we will denote these eight parameters for a given cosmology (see 
Section \ref{sec:data}) as $\psi \in \mathbb{R}^8$. 
Figure \ref{fig:mean_PCs_oneW} illustrates this decomposition with the estimated 
mean trend, the principal components contained in $B$, and one example of how the 
weight for the first PC will vary dependent on the first of $p_\psi=8$ cosmological 
parameters contained in $\psi$.

@@

From our 32 posterior means using DGP.FCO, these are input into SEPIA in order to predict power spectra
for the 32 test cosmologies. With the infinite-resolution output, we have a sense of the ``best-case" 
predictions we can have (i.e., if we trained with the 32 true power spectra, as opposed to our 
estimated posterior means). In Figure \ref{fig:pca_preds_v_camb}, we see comparisons of the heldout 
infinite resolution alongside two predictions: one based on DGP.FCO and the ``best-case" scenario using the
infinite-resolution spectra of the training set. There is a high level of agreement between the pairs
of predictions across cosmologies. Upon comparing MSEs for each of these prediction scenarios 
(Figure \ref{fig:mse_camb}, most are very similar across the two groups (with the two most difficult 
predictions being the exceptions), suggesting that overall DGP.FCO is estimating the true spectra 
for each batch well.

\begin{figure}
    \centering
    \includegraphics[width=4in]{preds_diff1_4_8.jpg}
    \caption{Predictions for 16 of the 32 test cosmologies after centering and scaling. 
             The interpolated infinite resolution run is shown in black, the prediction 
             (trained on the infinite resolution) is in blue and the prediction from 
             the DGP.FCO posterior mean is in red.}   
    \label{fig:pca_preds_v_camb}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=3in]{mse_dot.jpg}
    \caption{Comparison of MSE for CAMB predictions, when training with DGP.FCO posterior 
             means (left), and training with the ``true" infinite-resolution spectra (right).}   
    \label{fig:mse_camb}
\end{figure}

@@

Both Cosmic Emu and DGP.FCO are capable of modeling a true underlying functions based 
upon multiple functional realizations, but our approach utilizes DGPs within a 
hierarchical model in lieu of deep process convolutions. After obtaining the estimated 
smooth spectra from the training cosmologies, each method utilizes GPs in order to 
estimate the weights of the PCs from the estimated spectra. Below, we compare prediction 
performance between Cosmic Emu and DGP.FCO for the 6 held-out cosmologies. 
\textcolor{magenta}{In addition, we can also predict over a large uniform or full 
factorial design to obtain estimated main effects for each cosmological parameter in 
$\psi$, interactions amongst the $p_\psi=8$ parameters, and decompose the overall 
variation by main effects, two-way interactions, and so on. Should this be included?}

Plots for the average root mean squared error (RMSE) for each prediction method over the 
6 cosmologies and each $k$ value are shown in Figure \ref{fig:plot_rmse_k}. Comparisons 
of the spectrum estimation for training cosmologies are shown as well (using RMSE against 
the weighted average of observations). For predictions, DGP.FCO achieves the greatest 
reduction in RMSE in the region where perturbation theory and the low-resolution runs 
are deemed unbiased. For the region where only the high-resolution run is unbiased, 
Cosmic Emu has a lower average RMSE. Over all $k$ values and predictions, DGP.FCO has 
an average RMSE of 0.0089 and Cosmic Emu has an average RMSE of 0.0106. Our RMSE is 
lower at 56\% of $k$ values considered. The individual predictions for each method and 
cosmology are shown in Figure \ref{fig:plot_pred_1to6}.

@@

Multiple avenues for future research emerge: in addition to estimating dark matter 
power spectra, batches of hydrodynamical simulations exist, and this method could 
easily be adapted to handle such datasets. Other applications outside of cosmology 
can be explored, wherever multiple functional outputs exist, perhaps with spatial 
correlation (for example, observing multiple tropical cyclone forecasts). More detailed 
sensitivity analyses for the cosmological parameters can be explored to gain insights 
into how each of these parameters interact, and which are most significant. From a 
modeling perspective, changes to the model could include modeling the latent layer 
$W$ jointly across different cosmologies, as well as considering different redshift 
values other than $z=0$. Leveraging a hybrid model between DGP.FCO and Cosmic Emu 
may also help to obtain accurate estimates on the lower and higher ends of $k$ values, 
respectively. Additionally, Bayesian smoothing spline ANOVA (BSS-ANOVA) or other methods 
could be compared in addition to DGPs.

\section{Acknowledgments}
\label{sec:ack}

\textcolor{red}{This work was in part supported by the U.S. Department
of Energy, Office of Science, Office of Advanced Scientific Computing Research, 
Scientific Discovery through Advanced Computing (SciDAC) program through 
Grant 420453 "Enabling Cosmic Discoveries in the Exascale Era."}

The authors are pleased to acknowledge Advanced Research Computing at Virginia Tech 
(\url{https://arc.vt.edu/}) as well as the Shared Computing Cluster (SCC) administered
by Boston University's Research Computing Services (\url{www.bu.edu/tech/support/research/})
for providing computational resources and technical support that have contributed 
to the results reported within this paper.

@@

\begin{figure}[ht]
    \centering
    \includegraphics[width=6in]{pred_1to6.png}
    \caption{Results of all six predictions for both methods on the held-out 
    cosmologies (weighted average subtracted). CosmicEMU is dashed, DGP.FCO is dotted, 
    and solid gray lines show results of held-out computer model runs.}
    \label{fig:plot_pred_1to6}
\end{figure}

\section{Simulation Study Additional Results}
\label{sec:apdx_sims}
